The 2- and 3-point surface correlation functions calculations: from novel exact continuous approach to improving methodology for discrete images

### 2023-05-18 paper.tex
Remove enumitem package

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[export]{adjustbox}
\usepackage{hyperref}
\usepackage[inline]{enumitem}
\usepackage{resizegather}
\usepackage{cleveref}

@@

\subsection{Betterment of the discrete approach with improved edge filter}
In this work, in addition to filter $H$, we propose an improved filter $H'$. The
rationale behind this improvement is that:
\begin{enumerate*}[label=\alph*)]
\item a filter of width 3 may turn to be too narrow to give a good approximation
  for particular structures;
\item filter $H$ is not invariant under rotations, i.e.
  $H*R(A) \ne R(H*A)$, where $R$ is a rotation operator.
\end{enumerate*}
Filter $H'$ has a length $7$ and all coefficients with exception to the central
coefficient are inversely proportional to the distance from the center:
\begin{equation}
  \begin{aligned}
    H'_{ij} &= S \left\{
    \begin{array}{cc}
      \frac{1}{\sqrt{(i-3)^2 + (j-3)^2}} & \quad i \ne 3, j \ne 3 \\
      C & \quad \text{otherwise}
    \end{array}
    \right. \\
    H'_{ijk} &= S \left\{
    \begin{array}{cc}
      \frac{1}{\sqrt{(i-3)^2 + (j-3)^2 + (k-3)^3}} & \quad i \ne 3, j \ne 3, k
      \ne 3 \\
      C & \quad \text{otherwise}
    \end{array}
    \right.
  \end{aligned}
  \label{eq:filter-7x7}
\end{equation}
where $C$ is such that all coefficients of $H'$ sum to zero, and $S$ equals to
$30.45849$ in 2D and $172.96232$ in 3D case.

>>>>

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{xcolor}
\usepackage{algpseudocode}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage[export]{adjustbox}
\usepackage{hyperref}
\usepackage{resizegather}
\usepackage{cleveref}

@@

\subsection{Betterment of the discrete approach with improved edge filter}
In this work, in addition to filter $H$, we propose an improved filter $H'$. The
rationale behind this improvement is that:
\begin{itemize}
\item a filter of width 3 may turn to be too narrow to give a good approximation
  for particular structures;
\item The filter $H$ is not invariant under rotations, i.e.
  $H*R(A) \ne R(H*A)$, where $R$ is a rotation operator.
\end{itemize}
Filter $H'$ has a length $7$ and all coefficients with exception to the central
coefficient are inversely proportional to the distance from the center:
\begin{equation}
  \begin{aligned}
    H'_{ij} &= S \left\{
    \begin{array}{cc}
      \frac{1}{\sqrt{(i-3)^2 + (j-3)^2}} & \quad i \ne 3, j \ne 3 \\
      C & \quad \text{otherwise}
    \end{array}
    \right. \\
    H'_{ijk} &= S \left\{
    \begin{array}{cc}
      \frac{1}{\sqrt{(i-3)^2 + (j-3)^2 + (k-3)^3}} & \quad i \ne 3, j \ne 3, k
      \ne 3 \\
      C & \quad \text{otherwise}
    \end{array}
    \right.
  \end{aligned}
  \label{eq:filter-7x7}
\end{equation}
where $C$ is such that all coefficients of $H'$ sum to zero, and $S$ equals to
$30.45849$ in 2D and $172.96232$ in 3D case.
